On the specific recursive structure of iterated parametricity

### 2025-11-11 paper/paper.tex
Experimenting abbreviating deps already in the mutual definition of frame and restrftype

Assuming $\framep[n][0,...,p-1]$ and $\painting[n][0,...,p-1]$,
we can mutually define the types $\restrftype[n][0,...,p-1]$ of frame
restrictions together with $\framep[n+1][0,...p]$ as a function
from $\restrf[n][0,...,p-1]$, using auxiliary definitions for the
types and definitions of layers:

@@

              \restrf[n][0,...,p-1]:\restrftype[n][0,...,p-1]

@@

            \end{array}\right) & :      & \frametype[n+1][0,...,p]                             \\

@@

            \end{array}\right)                                                                 & \defeq & (\unitpoint,unit) \\

@@

              \restrf[n][0,...,p]   \\

@@

@@

                  \restrf[n+1][0,...,p-1]   \\
                \end{array}\right).\, \\

@@

                  \restrf[n][0,...,p]   \\
                \end{array}\right)(d) \\

@@

              \framep[n][0,...,p]:\frametype[n][0,...,p]        \\
              \painting[n][0,...,p]:\paintingtype[n][0,...,p]   \\
              \restrf[n][0,...,p]:\restrftype[n][0,...,p] \\

@@

              \restrf[n][0,...,p] \\

@@

            \end{array}\right) \rightarrow \U                                                                               \\

@@

              \framep[n][0,...,p]:\frametype[n][0,...,p]        \\
              \painting[n][0,...,p]:\paintingtype[n][0,...,p]   \\
              \restrf[n][0,...,p]:\restrftype[n][0,...,p] \\
            \end{array}\right)                                   & :      & \layertype[n][p]
              \framep[n][0,...,p]:\frametype[n][0,...,p]        \\
              \painting[n][0,...,p]:\paintingtype[n][0,...,p]   \\
              \restrf[n][0,...,p]:\restrftype[n][0,...,p] \\

@@

              \restrf[n][0,...,p] \\
    d \mapsto \Pi\omega.\,\painting[n][p](\restrf[n][p](d))

@@

At this stage, it is convenient to use an abbreviation to combine sequences $\framep[n][0,..,p-1]$, $\painting[n][0,...,p-1]$ and $\restrf[n][0,...,p-1]$ in one block, which we call $\depstype[n][0,...p-1]$:

\begin{align*}
  \depstype[n][0,..,p-1] \defeq
  \left(\begin{array}{lll}
            \framep[n][0,...,p-1]   & : & \frametype[n][0,...,p-1]    \\
            \painting[n][0,...,p-1] & : & \paintingtype[n][0,...,p-1]
            (\framep[n][0,...,p-1])                                   \\
            \restrf[n][0,...,p-1]   & : & \restrftype[n][0,...,p-1]
            \left(\begin{array}{l}
                \framep[n][0,...,p-1]   \\
                \painting[n][0,...,p-1] \\
              \end{array}\right)                             \\
          \end{array}\right)
\end{align*}
so that the type of $\framep[n+1][0,...,p]$ can be shortened into $\depstype[n][0,..,p-1] \rightarrow \frametype[n+1][0,...,p]$ and similarly for $\layertype[n][p]$ and $\layer[n][p]$.
Later, we shall write $\deps.\framep$, $\deps.\painting$, $\deps.\restrf$ for the corresponding projections of a $\deps$. By abuse of notation, we also write $\unitpoint$ for the only inhabitant of $\depstype[n][0,..,0-1]$.

>>>>

Assuming $\framep[n][0,...,p-1]$ and $\painting[n][0,...,p-1]$, we can
mutually define the types $\restrftype[n][0,...,p-1]$ of frame
restrictions together with $\framep[n+1][0,...p]$ as a function from
$\restrf[n][0,...,p-1]$, introducing also abbreviations for the types
and definitions of layers, as well as for the combination of sequences
of $\framep[n][0,..,p-1]$, $\painting[n][0,...,p-1]$ and
$\restrf[n][0,...,p-1]$ in one block, which we call
$\depstype[n][0,...p-1]$:

@@

    \depstype[n][0,..,p-1] & \defeq &
    \left(\begin{array}{lll}
              \framep[n][0,...,p-1]   & : & \frametype[n][0,...,p-1]    \\
              \painting[n][0,...,p-1] & : & \paintingtype[n][0,...,p-1]
              (\framep[n][0,...,p-1])                                   \\
              \restrf[n][0,...,p-1]   & : & \restrftype[n][0,...,p-1]

@@

    (\deps[n][0,...,p-1]:\depstype[n][0,...,p-1]) & :      & \frametype[n+1][0,...,p]                             \\

@@

    (\unitpoint)                                                                 & \defeq & (\unitpoint,unit) \\

@@

    (\deps)                                                               & \defeq &

@@

              (\deps[n][0,...,p-1]), \\

@@

              (\deps[n][0,...,p-1]) \\

@@

              (\deps[n][0,...,p])
              (d) \\

@@

    (\deps[n][0,...,p]:\depstype[n][0,...,p])

@@

    (\deps[n][0,...,p])

@@

    (\deps[n][0,...,p-1])
    \rightarrow \U                                                                               \\

@@

    (\deps[n][0,...,p]:\depstype[n][0,...,p])
    & :      & \layertype[n][p]
    (\deps[n][0,...,p])

@@

    (\deps[n][0,...,p])
    d \mapsto \Pi\omega.\,\painting[n][p](\restrf[n][p](d))\\

@@

Later, we shall write $\deps.\framep$, $\deps.\painting$, $\deps.\restrf$ for the projections of a $\deps$. Note that by abuse of notation, we also write $\unitpoint$ for the only inhabitant of $\depstype[n][0,..,0-1]$.
